Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2016-11-30 paper.tex
Add spectral assumptions to get J(eps) from J

It is customary to approximate the scattering kernel to linear order in
$\omega$ (as in~\cite[Eqn.~4.21]{shib2011-truncated_moment}):
\begin{equation}
  \label{eqn:se_kernel_expansion}
  R_{{\rm SE},i}(\varepsilon,\omega) \approx
  R_{{\rm SE},i}^0(\varepsilon) + \omega \, R_{{\rm SE},i}^1(\varepsilon),
\end{equation}
which allows us to write Eqns.~\ref{eqn:se_factor} and \ref{eqn:se_opacity} as
\begin{align}
  \label{eqn:se_factor_expansion}
  \Phi_{{\rm SE},i}(\varepsilon) &= \frac{1}{\mathscr{K}_{{\rm SE},i}}
  \big(R_{{\rm SE},i}^0(\varepsilon) J(\varepsilon) +
   R_{{\rm SE},i}^1(\varepsilon) \ell_\alpha H^\alpha(\varepsilon) \big) \\
  \label{eqn:se_opacity_expansion}
  \mathscr{K}_{{\rm SE},i}(\varepsilon) &=
  4\pi \frac{\varepsilon^3}{(2\pi)^3} R_{{\rm SE},i}^0(\varepsilon),
\end{align}
where we have made the energy-dependence explicit.

However, we don't know the energy dependence of $J(\varepsilon)$ and
$H^\alpha(\varepsilon)$,
since the the truncated moment simulations usually evolve only the integrated
moments, $J$ and $H^\alpha$.

>>>>

It is customary to approximate the scattering kernel to linear order in
$\omega$ (as in~\cite[Eqn.~4.21]{shib2011-truncated_moment}):
\begin{equation}
  \label{eqn:se_kernel_expansion}
  R_{{\rm SE},i}(\varepsilon,\omega) \approx
  R_{{\rm SE},i}^0(\varepsilon) + \omega \, R_{{\rm SE},i}^1(\varepsilon),
\end{equation}
which allows us to write Eqns.~\ref{eqn:se_factor} and \ref{eqn:se_opacity} as
\todo{drop anisotropic term and defend}
\begin{align}
  \label{eqn:se_factor_expansion}
  \Phi_{{\rm SE},i}(\varepsilon) &= \frac{1}{\mathscr{K}_{{\rm SE},i}}
  \big(R_{{\rm SE},i}^0(\varepsilon) J(\varepsilon) +
   R_{{\rm SE},i}^1(\varepsilon) \ell_\alpha H^\alpha(\varepsilon) \big) \\
  \label{eqn:se_opacity_expansion}
  \mathscr{K}_{{\rm SE},i}(\varepsilon) &=
  4\pi \frac{\varepsilon^3}{(2\pi)^3} R_{{\rm SE},i}^0(\varepsilon),
\end{align}
where we have made the energy-dependence explicit.

However, we don't know the energy dependence of $J(\varepsilon)$ and
$H^\alpha(\varepsilon)$ in general,
since simulations usually employ a gray moment scheme,
evolving only the energy-integrated moments, $J$ and $H^\alpha$
and sometimes $G$.
Nevertheless, we may reconstruct these energy-dependent source terms
from the gray moments by assuming a diluted Fermi-Dirac spectrum.

We use the following procedure:
\begin{enumerate}
\item
  Interpolate the equilibrium neutrino chemical potential, $\mu_\nu$,
  from the simulation grid.
\item
  Interpolate $J$ and $G$ from the simulation grid and
  compute the average neutrino energy in the fluid frame
  $\langle \varepsilon \rangle \equiv J/G$.
\item
  Compute the neutrino spectral temperature
  \begin{equation}
    T_\nu = \langle \varepsilon \rangle
    \frac{\mathscr{F}_3(\mu_\nu/T)}{\mathscr{F}_2(\mu_\nu/T)},
  \end{equation}
  where $\mathscr{F}_j$ is the Fermi integral
  \begin{equation}
    \mathscr{F}_j(\eta) = \int_0^\infty dx \, x^j (1+e^{x-\eta})^{-1}.
  \end{equation}
\item
  Assume the background neutrino fields have the same total density
  as the evolved moments
  \begin{align}
    J(\varepsilon) &=
    \frac{J}{\mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}, \\
    H^\mu(\varepsilon) &=
    \frac{H^\mu}{\mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}.
  \end{align}
\end{enumerate}
